Active Learning from Blackbox to Timed Connectors

### 2016-01-12 paper/paper.tex
.

In the past few years, researchers have been focusing on this area, and come up with a
series of impressive works. 
\todo{a list}
However, most of these works are based on models, instead of binaries. Then it comes a well-known
problem: \emph{how can we obtain these models?}

@@

% it seems that we need a graph to describe how we're doing this work
\todo{better graph}
\input{images/flow.tex}

@@

Reo is a channel based exogenous coordination language proposed by F. Arbab. 
A Reo model, also called \emph{connector}, provides the protocol
that formalizes the communication, synchronization and cooperation among the components which
communicate through the connector. Connectors can be defined with no knowledge of the components,
which makes Reo a powerful ``glue language'' in component-based
development\cite{DBLP:journals/sigsoft/Gill03}.

@@

As far as we can see, various forms of Mealy machines are defined in different works, wherein some
are deterministic and some are not. Since active automata learning very much depends on the system
under learning to be deterministic, in this paper we formally define a deterministic version of
Mealy machine following \cite{DBLP:conf/sfm/SteffenHM11}.

@@

\subsection{Time Domain}
Time is involved in several extension version of Reo. For example, Timed
Reo\cite{DBLP:conf/sefm/ArbabBBR04}, Hybrid Reo\cite{DBLP:conf/icfem/ChenSS14}, etc.
Generally, these models are designed to handle real-time behavior where time is defined in
$\mathbb{R}$. However, we also found a lot of works where authors use rational time to make things
easier.

In this paper, we choose the rational number field $\mathbb{Q}$ as our time domain, which simplifies
discretization of timed behaviors greatly.

>>>>

Distributed real-time embedded system (DRES) is reforming our lives with the name \emph{IoT}, the
internet of things, wherein systems are usually composed of individual components and a middleware
serving as a \emph{connector}. Such systems could be distributed logically or physically, which
makes the coordination even more complicated. In this case, we need to specify these coordination
processes with so-called \emph{coordination languages}, so that formal techniques can be applied to
guarantee their reliability.

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{./images/IoT.png}
  \end{center}
  \caption{Inter of Things in Our Life}
  \label{fig:IoT}
\end{figure}

researchers have been focusing on this area, and come up with a series of impressive works.
\todo{a list}
However, most of these works are based on models, instead of binaries. Then it comes a well-known
problem: \emph{how can we obtain these models?}

\emph{Correctness} of connectors is very much related to some low-level implementation details.
For example, well-writen code may behave dramatically weird with an improper set of concurrency
primitives. Such things happen frequently in embedded systems with different hardware platforms or
operating systems. Consequently, manually modeling a existing connector seems rather unreliable,
even with reference to its source code.

In this paper, we proposed a active learning framework to automatically extract timed connectors
from blackbox models.

@@

% it seems that we need a graph to describe how we're doing this work
\todo{better graph}
% \input{images/flow.tex}

@@

Reo is a channel based exogenous coordination language proposed by F. Arbab in
\cite{DBLP:journals/mscs/Arbab04}. 
A Reo model, also called \emph{connector}, provides the protocol
that formalizes the communication, synchronization and cooperation among the components which
communicate through the connector. Connectors can be defined with no knowledge of the components,
which makes Reo a powerful ``glue language'' in component-based
development\cite{DBLP:journals/sigsoft/Gill03}.

@@

As far as we can see, various forms of Mealy machines are defined in different works, wherein some
are deterministic and some are not. Since active automata learning very much depends on the
system-under-learn to be deterministic, in this paper we formally define a deterministic version of
Mealy machine following \cite{DBLP:conf/sfm/SteffenHM11}.

@@

\subsection{Time Domain}
Time is involved in several extension version of Reo. For example, Timed
Reo\cite{DBLP:conf/sefm/ArbabBBR04}, Hybrid Reo\cite{DBLP:conf/icfem/ChenSS14}, etc.
Generally, these models are designed to handle real-time behavior where time is defined in
$\mathbb{R}$. Besides, we also found some works\cite{DBLP:journals/fmsd/PrabhakarDM015} rational
time is chosen to make things easier. In this paper, we choose the rational number field
$\mathbb{Q}$ as our time domain, which simplifies discretization of timed behaviors greatly.
